---
title: "Q2final-model"
author: "Xin Zou"
date: "Dec 1, 2017"
output: word_document
---

#set work directory
```{r}
setwd("~/Downloads")
View(Q2data1)
View(Q2data2)
```
#Summary Statistics
#For 2012 yr training model
```{r}
print(summary(Q2data1)) #X1 is only the number of the row, it means nothing
hist(Q2data1$est_income_code) # It is likely a normal distribution
hist(Q2data1$SA_RateofPay)
hist(log(Q2data1$SA_RateofPay)) # The log transformed not seems to change to much

Q2data1$return_amount2012=Q2data1$`2012return_amount`
Q2data2$return_amount2013=Q2data2$`2013return_amount`
Q2data2$return_amount2012=Q2data2$`2012return_amount`
table(Q2data1$MallGrade)
Q2data1$Amall=ifelse(Q2data1$MallGrade=="A",1,0) # We set Mall B as reference
Q2data1$Cmall=ifelse(Q2data1$MallGrade=="C",1,0)
Q2data1$Fmall=ifelse(Q2data1$MallGrade=="F",1,0)


# For 2013 yr training model
Q2data2$MajorCompetitorPresent<-as.numeric(Q2data2$MajorCompetitorPresent)
print(summary(Q2data2))
hist(Q2data2$est_income_code)
hist(Q2data2$SA_RateofPay)
hist(log(Q2data2$SA_RateofPay))
hist(Q2data1$`2012return_amount`)
hist(log(1+Q2data1$`2012return_amount`)) #Use the log-transformed
Q2data2$Amall=ifelse(Q2data2$MallGrade=="A",1,0) # Set Mall B as reference
Q2data2$Cmall=ifelse(Q2data2$MallGrade=="C",1,0)
Q2data2$Fmall=ifelse(Q2data2$MallGrade=="F",1,0)
hist(Q2data1$`2012sales`)
hist(log(1+Q2data1$`2012sales`)) #Use the log for sales
Q2data1$sales2012<-log(1+Q2data1$`2012sales`)# We should use the log for sales to get a normal distribution 
Q2data1$return_amount2012<-log(1+Q2data1$`2012return_amount`)
Q2data2$return_amount2013<-log(1+Q2data2$`2013return_amount`)
Q2data2$return_amount2012<-log(1+Q2data2$`2012return_amount`)
# Run the model
# Model 2012
# After tested several models
Q2model4<-lm(return_amount2012~training2012+sales2012+est_income_code+SA_YearsofService+MallSalesSF+TotalCases+StoreSqFt+MajorCompetitorPresent+homeowner_code+I(SA_YearsofService^2),data = Q2data1)
print(summary(Q2model4))# We think that the years of service of salesmen will have a curve influence on return amount, so use a quadratic term
# We also found that whether the employee is full time or part time will have diffrent slopes for the results, so we include the interaction term

Q2model8<-lm(return_amount2012~training2012*SA_AssignmentCategory+sales2012+est_income_code+SA_YearsofService+MallSalesSF+TotalCases+StoreSqFt+MajorCompetitorPresent+homeowner_code+I(SA_YearsofService^2),data = Q2data1)
print(summary(Q2model8)) # We can see that the training wil help to decrease the return, and Full time employees have more impact on this process
anova(Q2model4,Q2model8,test="Chisq") #The result shows that model8 is better, because it is significant

# Model 2013
# After tested several models
Q2model11<-lm(return_amount2013~training2013+training2013*training2012+MajorCompetitorPresent+SA_AssignmentCategory+TotalCases+I(SA_YearsofService^2)+SA_YearsofService+est_income_code+homeowner_code,data = Q2data2)
print(summary(Q2model11))
Q2model12<-lm(return_amount2013~training2013*SA_AssignmentCategory+training2013*training2012+MajorCompetitorPresent+SA_AssignmentCategory+TotalCases+I(SA_YearsofService^2)+SA_YearsofService+est_income_code+homeowner_code,data = Q2data2) # The same with the year 2012, but add the interaction term for Training2012 and Training2013, because whether people took the training last year will influence the slope for the next year.
print(summary(Q2model12))
anova(Q2model11,Q2model12,test="Chisq") # It is significant, so we should use model12
# The results show that the impact of tarining in 2013 is less significant comparing the last year.And still full time have more impact for training and return



#Check Multicollineary
library(usdm)
df=data.frame(Q2data1$est_income_code,Q2data1$SA_YearsofService,Q2data1$MallSalesSF,Q2data1$TotalCases,Q2data1$StoreSqFt,Q2data1$MajorCompetitorPresent,Q2data1$homeowner_code)
cor(df) # There are no serious correlationship in there variables
vif(df)  #We found that there are no multicallinearity
df1=data.frame(Q2data2$training2013,Q2data2$training2012,Q2data2$MajorCompetitorPresent,Q2data2$SA_AssignmentCategory,Q2data2$TotalCases,Q2data2$SA_YearsofService,Q2data2$est_income_code,Q2data2$homeowner_code)
cor(df1) # There are no serious correlationship in there variables
vif(df1) #We found that there are no multicallinearity

#Check Hetoroskedasticity
pred<-predict(Q2model8)
res1=resid(Q2model8)
plot(pred,res1,ylab="Residuals",xlab="Fitted values") #We saw a pattern
library(lmtest)
gqtest(Q2model8)
bptest(Q2model8) # The F-statistics of P value is significant,so there is Heteroskedasticity
library(sandwich)
library(foreign)
coeftest(Q2model8,vcov=vcovHC(Q2model8),"HC1" ) #We should use the robust standard error
# The same with year 2013
pred<-predict(Q2model12)
res2=resid(Q2model12)
plot(pred,res2,ylab="Residuals",xlab="Fitted values")
library(lmtest)
gqtest(Q2model12)
bptest(Q2model12)
library(sandwich)
library(foreign)
coeftest(Q2model12,vcov=vcovHC(Q2model12),"HC1" )

# Interpret the results
library(effects)
plot(effect(term="SA_YearsofService",mod=Q2model8))
plot(effect(term = "training2012:SA_AssignmentCategory",mod = Q2model8,default.levels=2,multiline=TRUE)) #We want to all the lines in one plot
plot(effect(term = "training2012:SA_AssignmentCategory",mod = Q2model8,xlevels=2),multiline=TRUE) #The result shows that the more training they have, full time salesmen increased the return amount and part time decreased the amount

library(effects)
plot(effect(term="SA_YearsofService",mod=Q2model12))
plot(effect(term = "training2013:SA_AssignmentCategory",mod = Q2model12,xlevels=2),multiline=TRUE) # The result shows that training 2013 will lead to both fulltime and partime salesmen increase the retrun amount, but the impact for full time is more serious
```
# Check for Endogenity
# Since training is decided by salesmen, we consider there might be endogenity, and the pressures form their family will push them to take the training.So the SA_MartialStatus and SA_Dependent is the best instruments, because they are correlated with training but have no relation with return amount.
```{r}
library(AER)
library(foreign)
Q2model15<-ivreg(return_amount2012~training2012*SA_AssignmentCategory+sales2012+est_income_code+SA_YearsofService+MallSalesSF+TotalCases+StoreSqFt+MajorCompetitorPresent+homeowner_code+I(SA_YearsofService^2)|SA_MartialStatus+SA_MartialStatus*SA_AssignmentCategory+SA_Dependent+SA_Dependent*SA_AssignmentCategory+sales2012+est_income_code+SA_YearsofService+MallSalesSF+TotalCases+StoreSqFt+MajorCompetitorPresent+homeowner_code+I(SA_YearsofService^2),data = Q2data1)
summary(Q2model15,diagnostics=TRUE)
Q2model116<-ivreg(return_amount2013~training2013*SA_AssignmentCategory+training2013*training2012+MajorCompetitorPresent+SA_AssignmentCategory+TotalCases+I(SA_YearsofService^2)+SA_YearsofService+est_income_code+homeowner_code|SA_MartialStatus+SA_MartialStatus*SA_AssignmentCategory+SA_MartialStatus*training2012+MajorCompetitorPresent+SA_AssignmentCategory+TotalCases+I(SA_YearsofService^2)+SA_YearsofService+est_income_code+homeowner_code,data = Q2data2)
summary(Q2model16,diagnostics=TRUE)
# From the results, the instruments did not pass the first stage test, it means the instruments can not justify regerence assumption. So they are not good. Do not apply endogenity.
```
